\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-05-06 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added a comment about fluid-solid matching inside the CPML; also restored doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.pdf, which needs to be there because it is used on the CIG web site (the link to the manual points to this SVN file; thus please do NOT remove it)

This new release of the code (version 2.1) includes support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10,Kom11}.\\

The next release of the code will include support Convolution or Auxiliary Differential Equation Perfectly Matched absorbing Layers
(C-PML or ADE-PML) \citep{MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10,KoMa07}.
It will also use the PT-SCOTCH parallel and threaded version of SCOTCH for mesh partitioning instead of the serial version.\\

@@

>>>>

This new release of the code (version 2.1)
includes Convolution or Auxiliary Differential Equation Perfectly Matched absorbing Layers
(C-PML or ADE-PML) \citep{MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10,KoMa07}.
It also includes support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10,Kom11}.\\

The next release of the code will use the PT-SCOTCH parallel and threaded version of SCOTCH for mesh partitioning instead of the serial version.\\

@@

Note: in the case of fluid-solid layers in contact, the fluid-solid interface currently needs to be flat and horizontal
inside the CPML layer (i.e., bathymetry should become flat and horizontal when entering the CPML); this (small) constraint
will probably remain in the code for a while because it makes fluid-solid matching inside the CPML much easier.
